\section{Team Work and One Year Horizon}
The proposed project requires expertise in large-scale application profiling, operating systems, and computer architectures. Our team has full knowledge and strong experiences to succeed. Kevin had worked on platform architecture definitions, OS kernel developments, and the performance optimization of smartphone SoC in the industry for 5 years. These experiences will be helpful for the characterization of the applications, the design of the low-cost PIM modules, and the architecture of the virtual address scheme. Amirali had worked on computer architecture researches for 3 years and will focus on the system simulation modeling and the design of the efficient cache coherence schemes. Our advisor Onur Mutlu will definitely provide his advice throughout the whole project. 

In our plan, the first step is to define the PIM functions. In the first month, we plan to do the characterization of the in-memory database in a real system and prepare the simulation infrastructure. In the following 2 months, we plan to design the low-cost PIM functions in the simulator based on the finding of the characterization and do extensive evaluations.

The second step is to tackle the challenges of virtual address translation and cache coherence. From the fourth to the eighth month, we will design the virtual address scheme and the cache coherence mechanisms, implement them in the simulator and verilog, and rigorously evaluate their benefits and overheads.

The last step is to make sure the PIM functions are general enough for other applications. We will evaluate other applications, such as memcached~\cite{fitzpatrick2004distributed} or image analysis applications, to verify the consistent performance improvements. We plan to work toward this goal until the end of eleventh month, and wrap up everything for publication in the final month.
